Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-01-27 paper/main.tex
anterior vs posterior PPA

\todo[inline]{at the moment positioned here; makes sense at a couple of other
positions; not shure yet}

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type (cf. Epstein (1998, 1999, 2003,
2008).\todo{check references}
% we did not choose se\_new and se\_old
In the current study we did not include the categories that contained switches
from one setting to another (\texttt{se\_new} and \texttt{se\_old}) which one
might assume to contain the auditory equivalent to the ``optimal'' visual
stimulus type in the primary contrast.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[in a] football stadium'', ``[Forrest is running through
the] jungle'') but mostly landmarks or buildings and also non-spatial hints
(e.g. ``[Jenny as a] teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if holistic but also vague verbal descriptions of landscapes lead to
a different hemodynamic activity level than more concrete descriptions of a
landscape's content (e.g.``[a] beacon'', [a] ``farmhouse'', ``[an] apartment
building'').

@@

\subsection{Robust (results) across contrasts}

@@

\todo[inline]{despite ad hoc approach in movie, ``non-perfect'' speech-anno,
and non-exhausting confound control, we have a pattern of spatially restricted
clusters across contrasts (and stimuli)}

% more than just one contrast
For both naturalistic stimuli, we computed several $t$-contrasts that differed
in the contrasted categories of stimulus features and the amount of available
data to test the robustness of our findings.
% why we did a couple of contrasts
m.a.w.: For both stimuli we created several contrasts that varied the amount of
events available for the analysis and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.

@@

% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but also extending into more posterior brain
regions

% PPA AD
Regarding contrasts of the AD stimulus, six of eight contrasts show significant
bilateral clusters in the anterior part of the group PPA overlap.

% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust across contrasts do not depend on the design of one specific
contrasts.

% but
Nevertheless, results are still influenced by [sensitive to] the amount of
available data and how well the feature space is modeled.
% example
For example, contrast 8 of the AD stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a stimulus to be chosen may provide and how homogeneous the events to be
averaged might be.

\subsubsection{anterior vs. posterior PPA}

@@

% intro
Results of the AD contrasts consistently yielded significant clusters spatially
constrained to the anterior part of the PPA group overlap [and to the anterior
part of significant clusters of the AV contrasts].
% PPA might have submodules
Previous studies provide evidence that the PPA can be devided into functionally
subregions that might process different stimulus features [during visual scene
perception].
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to the hypothesis by \citep{baldassano2013differential} the PPA
consists of subregions that activate selectively to scenes and ``cooperate to
build a complete representation of a scene''.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.
Our results add further evidence that the PPA is not a homogeneous area but can
be devided into functionally subregions.
% pPPA
Results of your study suggest that the pPPA is more concerned with visual
aspects of spatial information as exclusively inherent in visual stimuli like
pictures or movies.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) inherent in both visual and
verbal stimuli.

@@

\todo[inline]{makes sense because it goes full circle to general naturalistic
stimulus topic and makes transition to negative controls easier}

@@

@@

\subsubsection{shower tought: changes in soundscape should also correlate with
PPA activity}

@@

\begin{itemize}
\item We reuse public data for independent research question
\item GLM based on annotations to operationalize ``spatial perception''
\item Our results add evidence that model-driven analyses based in annotations
can be run on data from naturalistic stimuli to ``localize'' brain activity
correlating with specific perceptual processes.
\item ``localization performance'' relies on how well the model captures
different aspects of the stimuli's feature space.
\item PPA is functionally heterogenous region
\item a complex but naturally engaging auditory stimulus like an
audiobook might in principle be used as a non-visual localizer for a variety of
brain functions in subjects who are not willing or able to follow task
instructions during brain scanning [would state that explicitly in the summary
at the end].
\end{itemize}

>>>>

\todo[inline]{at the moment positioned here; makes sense at a couple of other
positions; not sure yet}

% optimal stimulus type in vision
In the visual domain, landscapes and not pictures of landmarks or buildings are
considered to be the ``optimal'' stimulus type
\citep{epstein2008parahippocampal}.\todo{a review}
% we did not choose se\_new and se\_old
We did not include the categories that contained switches from one setting to
another (\texttt{se\_new} and \texttt{se\_old}) which one might assume to
contain the auditory equivalent to the ``optimal'' visual stimulus type in the
primary AD contrast.
% why
The reason was that the categories \texttt{se\_new} and \texttt{se\_old} were
heterogeneous: they rarely contained holistic (but also vague) descriptions of
landscapes (e.g.  ``[in a] football stadium'', ``[Forrest is running through
the] jungle'') but mostly landmarks or buildings and also non-spatial hints
(e.g. ``[Jenny as a] teenager``).
% further studies
Given that humans can identify the gist of a rich visual scene within the
duration of a single fixation \citep{henderson2003human} further studies might
investigate if vague verbal descriptions of landscapes lead to a different
hemodynamic activity level than descriptions of more concrete parts of a scene
(e.g.``[a] beacon'', [a] ``farmhouse'').

@@

\subsection{Robust results across contrasts}

@@

% why we did a couple of contrasts
To test the robustness of our approach, we created several additional contrasts
for each naturalistic stimulus by varying the contrasted categories (and thus
the amount of available data), and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.

@@

% PPA AV
Regarding contrasts of the AV stimulus (see Table \label{tab:av-contrasts}), all
five AV contrasts show significant bilateral clusters in the PPA but also
extending into more posterior brain regions.
% PPA AD
Regarding contrasts of the AD stimulus (see Table \label{tab:ao-contrasts}), six
of overall eight contrasts show significant bilateral clusters in the anterior
part of the group PPA overlap.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust and do not depend on the design of one specific contrasts.
% but
Nevertheless, results are sensitive to the contrasted categories and the amount
of available data.
% example
For example, contrast 8 of the AD stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a naturalistic stimulus may provide and how homogeneous the events to be
averaged might be.

@@

% anterior vs posterior pattern
In contrasts 1 to 6 of the AD stimulus, we find consistently significant
clusters spatially constrained to the anterior part of the PPA group overlap as
defined by the visual localizer [as well as constrained to the anterior part of
significant cluster of AV contrasts].
% question
This raises the question if the different activation patterns can be attributed
to different features inherent in visual compared to verbal stimuli.
% visual scenes: probably submodules
In the domain of visual scene perception, previous studies provide evidence that
the PPA can be divided into functionally subregions that might process different
stimulus features.
% posterior: functionality
The posterior PPA (pPPA) is functionally more responsive than the anterior PPA
(aPPA) to low-level features of scenes or (abstract) objects
\citep{baldassano2013differential, nasr2014thinking,
rajimehr2011parahippocampal}.
% anterior cIPL is defined using the Eickhoff–Zilles PGp probabilistic
% cytoarchitectonic map
The aPPA is functionally more responsive than pPPA to high-level features of
scenes (e.g. real-word size \citep{park2015parametric}; a scene's abstract
identity/category \citep{marchette2015outside, watson2016patterns}) and objects
(e.g. spatial contextual associations \citep{aminoff2007parahippocampal,
aminoff2013role}).
% connectivity
Moreover, pPPA and aPPA show differences in connectivity profiles.
% posterior
The pPPA is more strongly functionally connected to the occipital visual cortex
than the aPPA \citep{baldassano2013differential, baldassano2016two}.
% including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
% anterior
The aPPA is more strongly functionally connected to portions of the default mode
network, including caudal inferior parietal lobe (cIPL), the restrosplenial
complex (RSC), medial PFC and the lateral surface of the anterior temporal lobe
\citep{baldassano2013differential, baldassano2016two}.
% conclusion: subregions
According to the hypothesis by \citep{baldassano2013differential} the PPA
consists of subregions that activate selectively to scenes and ``cooperate to
build a complete representation of a scene''.
% Their distinct connectivity properties do suggest that each may be involved in
% specific aspects of visual and cognitive processing involved in the
% overarching goal of scene understanding \citep{baldassano2013differential}.
% The fact that anterior PPA had a lower sensitivity to our abstract object
% stimuli does not necessarily imply that this region does not use object
% information \citep{baldassano2013differential}. Previous work has shown that
% PPA responds to objects that have spatial associations [Aminoff et al. 2007],
% are space-defining [Mullally and Maguire 2011], and are
% navigationally-relevant [Janzen and Van Turennout 2004]. These types of
% responses require spatial memory and cannot be based purely on visual features
% like object shape. \citep{baldassano2013differential}.
Our results add further evidence that the PPA is not a homogeneous area but can
be divided into functionally subregions.
% pPPA
Our results suggest that the pPPA is more concerned with visual aspects immanent
in pictures or movie shots of landscapes.
% aPPA
The aPPA might be more concerned with non-visual aspects of spatial information
(e.g. spatial contextual information \citep{aminoff2013role,
aminoff2015associative, baumann2016functional}) as immanent/inherent in both
visual and verbal stimuli.

@@

\todo[inline]{imo it should be possible to handle the following two subsections
    in one subsection; à la: GLM + naturalistic stimuli works because
    confounds average (most often) out AND negative control contrasts show
    negative results; except where features of AV + AD were correlated; but
that's actually cool because -> hypothesis}

@@

\todo[inline]{similarly: we have a pattern of spatially restricted clusters
across contrasts (and stimuli) in the PPA contrasts -> natural stimuli =
suitable}

@@

\subsubsection{shower thought: changes in soundscape should also correlate with
PPA activity}

@@

\begin{itemize}
\item We reuse public data for independent research question
\item GLM based on annotations to operationalize ``spatial perception''
\item Our results add evidence that model-driven analyses based in annotations
can be run on data from naturalistic stimuli to ``localize'' brain activity
correlating with specific perceptual processes.
\item ``localization performance'' relies on how well the model captures
different aspects of the stimuli's feature space.
\item PPA is functionally heterogeneous region
\item a complex but naturally engaging auditory stimulus like an
audiobook might in principle be used as a non-visual localizer for a variety of
brain functions in subjects who are not willing or able to follow task
instructions during brain scanning [would state that explicitly in the summary
at the end].
\end{itemize}
